Cloud Computing Data Capsule for Non-consumptive Text Analysis

### 2014-02-27 cloudpaper/paper.tex
More minor changes
settled on 'Data Capsules'

\numberofauthors{8}
\author{
\alignauthor
Jiaan Zeng \\
       \affaddr{School of Informatics and Computing Indiana University}\\
       \email{jiaazeng@indiana.edu}
\alignauthor
Guangchen Ruan \\
       \affaddr{School of Informatics and Computing Indiana University}\\
       \email{gruan@indiana.edu}
\alignauthor 
Alex Crowell \\
       \affaddr{Department of Computer Science and Engineering University of Michigan}\\
       \email{crowella@umich.edu}
\and  % use '\and' if you need 'another row' of author names
\alignauthor 
Atul Prakash \\
       \affaddr{Department of Computer Science and Engineering University of Michigan}\\
       \email{aprakash@umich.edu}
% 5th. author
\alignauthor Beth Plale \\
       \affaddr{School of Informatics and Computing Indiana University}\\
       \email{plale@indiana.edu}
}

@@

% A category with the (minimum) three required fields
\category{H.3.4}{Systems and Software}{Distributed Systems}[Cloud Computing, Storage Capsules]
%A category including the fourth, optional field follows...
\category{K.6.m}{Miscellaneous}{Security}[Non-consumptive Research]

@@

\keywords{Cloud computing, Large-scale Text Mining, Non-consumptive Research, Storage Capsules} % NOT required for Proceedings

@@

Storage capsules \cite{Borders:2009:PCD:1855768.1855791} is a mechanism for
containing sensitive data within a virtualized environment with the goal of
minimizing the available channels to leak that data.  Although storage capsules
provide no guarantees on the integrity of the stored data -- which could be
modified or deleted by an attacker -- this poses little issue when storage
capsules is applied to non-consumptive research, where the copyrighted source
data can simply be made read-only.  Additionally, the storage capsules design
is well-suited to non-consumptive research, in that it is able to maintain
strong security guarantees on the sensitive data while being highly permissive
to users, who may need to install custom software or perform other actions that
would require the granting of many privileges in a normal environment.  The
application of storage capsules we present in this paper currently does not
provide the same level of protection against covert channels that is provided
in the original storage capsules system, but improvements in the implementation
are being made that will eventually provide greater protection than that given
in the original work.

@@

\subsection{Storage Capsules}

Storage capsules is a system developed by Borders et al.
\cite{Borders:2009:PCD:1855768.1855791} that allows privileged access to
sensitive data while also restricting the channels through which that data can
be released.  Capsules uses virtual machine snapshotting and simple
policy-based restriction mechanisms to allow a user to enter a ``secure'' mode,
where network and other data channels are restricted in exchange for access to
the data being protected.  After using the protected data, when the user
returns to normal use of the system, which we call ``maintenance'' mode, all
changes to the system except those made to the designated secure data are
forgotten, and the system returns to the state it was in before the switch to
secure mode, thereby regaining full Internet access and the ability to make
persistent changes to the virtual machine, such as installing software.  In
this way, network and storage channels cannot be used to leak the sensitive
data.  This usage model is readily applicable to non-consumptive research, in
that a researcher can administer their system (e.g. install any required
software tools) and then switch to ``secure'' mode to perform their analysis.

Because storage capsules was originally developed with use on a personal
machine in mind, it had to be adapted and extended to work within the HTRC
cloud environment. In HTRC, sensitive data is copyrighted text that is exposed
through a Restful web service API instead of within a machine. Storage capsules
manages the network channel between virtual machines and the web services
serving data to them. In consideration of potential future HTRC services,
storage capsules has a flexible network control mechanism that allows network
policies for different modes to be written by administrators.

Additionally, in order to provide a cloud environment across multiple machines
and to a large number of researchers, there is a need for another layer on top
of storage capsules that coordinates different machines. We therefore
implemented a web service layer that is responsible for management of virtual
machines (e.g., resource allocation, request scheduling, status maintenance)
above the storage capsules layer.  Section \ref{title:design} gives details of
the design and implementation of storage capsules and the web service layer in
the context of HTRC.

@@

The backend that manages virtual machines is implemented as a set of Linux
shell scripts that manage the \texttt{qemu} VMM in order to implement the
functionality of storage capsules.  These scripts are remotely run by the web
service via a secure shell (SSH) connection.  \texttt{qemu} provides live
snapshotting functionality that serves an important role in realizing our
storage capsules implementation.  When a user transitions to secure mode, a
snapshot is taken of the entire virtual machine state via the backend scripts,
and any further use of the system is recorded in memory and does not persist
upon shutdown or any other operation.  Upon return to maintenance mode, the
snapshot taken earlier is restored, and all system progress that followed it is
forgotten.

>>>>

\numberofauthors{8}
\author{
\alignauthor
Jiaan Zeng \\
       \affaddr{School of Informatics and Computing Indiana University}\\
       \email{jiaazeng@indiana.edu}
\alignauthor
Guangchen Ruan \\
       \affaddr{School of Informatics and Computing Indiana University}\\
       \email{gruan@indiana.edu}
\alignauthor 
Alexander Crowell \\
       \affaddr{Department of Computer Science and Engineering University of Michigan}\\
       \email{crowella@umich.edu}
\and  % use '\and' if you need 'another row' of author names
\alignauthor 
Atul Prakash \\
       \affaddr{Department of Computer Science and Engineering University of Michigan}\\
       \email{aprakash@umich.edu}
% 5th. author
\alignauthor Beth Plale \\
       \affaddr{School of Informatics and Computing Indiana University}\\
       \email{plale@indiana.edu}
}

@@

% A category with the (minimum) three required fields
\category{H.3.4}{Systems and Software}{Distributed Systems}[Cloud Computing, Data Capsules]
%A category including the fourth, optional field follows...
\category{K.6.m}{Miscellaneous}{Security}[Non-consumptive Research]

@@

\keywords{Cloud computing, Large-scale Text Mining, Non-consumptive Research, Data Capsules} % NOT required for Proceedings

@@

Data capsules \cite{Borders:2009:PCD:1855768.1855791} is a mechanism for
containing sensitive data within a virtualized environment with the goal of
minimizing the available channels to leak that data.  Although data capsules
provide no guarantees on the integrity of the stored data -- which could be
modified or deleted by an attacker -- this poses little issue when data 
capsules is applied to non-consumptive research, where the copyrighted source
data can simply be made read-only.  Additionally, the data capsules design
is well-suited to non-consumptive research, in that it is able to maintain
strong security guarantees on the sensitive data while being highly permissive
to users, who may need to install custom software or perform other actions that
would require the granting of many privileges in a normal environment.  The
application of data capsules we present in this paper currently does not
provide the same level of protection against covert channels that is provided
in the original data capsules system, but improvements in the implementation
are being made that will eventually provide greater protection than that given
in the original work.

@@

\subsection{Data Capsules}

Data capsules is a system developed by Borders et al.
\cite{Borders:2009:PCD:1855768.1855791} that allows privileged access to
sensitive data while also restricting the channels through which that data can
be released.  Capsules uses virtual machine snapshotting and simple
policy-based restriction mechanisms to allow a user to enter a ``secure'' mode,
where network and other data channels are restricted in exchange for access to
the data being protected.  After using the protected data, when the user
returns to normal use of the system, which we call ``maintenance'' mode, all
changes to the system except those made to the designated secure data are
forgotten, and the system returns to the state it was in before the switch to
secure mode, thereby regaining full Internet access and the ability to make
persistent changes to the virtual machine, such as installing software.  In
this way, network and storage channels cannot be used to leak the sensitive
data.  This usage model is readily applicable to non-consumptive research, in
that a researcher can administer their system (e.g. install any required
software tools) and then switch to ``secure'' mode to perform their analysis.

Because data capsules was originally developed with use on a personal
machine in mind, it had to be adapted and extended to work within the HTRC
cloud environment. In HTRC, sensitive data is copyrighted text that is exposed
through a Restful web service API instead of within a machine. Data capsules
manages the network channel between virtual machines and the web services
serving data to them. In consideration of potential future HTRC services,
data capsules has a flexible network control mechanism that allows network
policies for different modes to be written by administrators.

Additionally, in order to provide a cloud environment across multiple machines
and to a large number of researchers, there is a need for another layer on top
of data capsules that coordinates different machines. We therefore
implemented a web service layer that is responsible for management of virtual
machines (e.g., resource allocation, request scheduling, status maintenance)
above the data capsules layer.  Section \ref{title:design} gives details of
the design and implementation of data capsules and the web service layer in
the context of HTRC.

@@

The backend that manages virtual machines is implemented as a set of Linux
shell scripts that manage the \texttt{qemu} VMM in order to implement the
functionality of data capsules.  These scripts are remotely run by the web
service via a secure shell (SSH) connection.  \texttt{qemu} provides live
snapshotting functionality that serves an important role in realizing our
data capsules implementation.  When a user transitions to secure mode, a
snapshot is taken of the entire virtual machine state via the backend scripts,
and any further use of the system is recorded in memory and does not persist
upon shutdown or any other operation.  Upon return to maintenance mode, the
snapshot taken earlier is restored, and all system progress that followed it is
forgotten.
